 Solving ODEs in R

### 2014-11-20 documentation/solving_ODEs.Rmd
run simulation of ODE system of Kefi et al 2007

## simulating over given $\rho_+$
For the project, we need a prediction of growth for a given value of $\rho_+$. To achieve this, I reformulate the ODE system to be a function of $\rho_+$, which I add to the list of parameters.

@@

odesys <- function (t, rho, parms = model_parms) {
  list(c(
    d_rho_pm(rho, parms),
    d_rho_pp(rho, parms),
    d_rho_mm(rho, parms),
    model_parms$rho_p,
    d_rho_m(rho, parms)
    ))
}

# initial vegetation cover
rho_ini <- 0.6
model_parms$rho_p <- rho_ini

@@

>>>>

## simulating over given $\rho_+$
For the project, we need a prediction of growth for a given value of $\rho_+$. To achieve this, I am simulating a gradient of replicates with different environmental conditions.

```{r, echo = FALSE}
library(foreach)
library(doSNOW)

workstation <-  list(host = "162.38.184.118", user = "schneider",
                     rscript = "/usr/lib/R/bin/Rscript",
                     snowlib = "/usr/lib/R/library")

workerlist <- c(rep("localhost", times = 10))

cl <- makeSOCKcluster(workerlist, master="162.38.184.88", outfile='out_messages.txt')

registerDoSNOW(cl)

@@

first_ID = 1  #

global <- list(  
  m = 0.1, #intrinsic mortality
  d = 0.1,    # degradation
  c = 0.2, 		# beta*g  
  delta = 0.1,  	# seeds dispersed; (1-del) seeds on nearest neighbourhood
  r = 0.01, 	# regeneration rate
  f = 0.9		# local fascilitation
)

parameters <- list(
  b = seq(0,1,.01) #seq(0,1,.002)+0.001
)

iterations <- expand.grid(parameters)
iterations <- cbind(ID = 1:dim(iterations)[1],iterations, global)
str(iterations)

@@

foreach(iteration = iterations$ID, .combine = rbind, .packages = c("deSolve")) %dopar% { 
 model_parms <- as.list(iterations[iteration,])

  # running the ode-solver
  runmodel <- ode(y = rho, func = odesys, times = c(1,60), parms = model_parms)

  # transfer into ouput and calculate missing rho values
  out <- as.data.frame(runmodel)
  out$rho_0 <- 1 - out$rho_p - out$rho_m
  out$rho_p0 <- with(out, rho_p-rho_pm-rho_pp)
  out$rho_m0 <- with(out, rho_m-rho_pm-rho_mm)
  out$rho_00 <- with(out, rho_0-rho_m0-rho_p0)
  out$ID <- iteration

  return(out[dim(out)[1],])
  } -> output

plot(output$rho_p ~ iterations$b, type = "l", ylim = c(0,1))

stopCluster(cl)
